Morphology-based Entity and Relational Entity Extraction Framework for Arabic

### 2018-06-27 tex/merf/TALMajor/tool.tex
merf: fit into 25 pages

For each MRE, 
\framework generates its equivalent non-deterministic finite automaton (NFA) in the typical manner~\cite{sipser2006introduction}.
%Each MRE operation has its equivalent representation in an NFA. 
We support the upto operation ($f$\^{}$x$), which is not directly 
supported in~\cite{sipser2006introduction}, by 
%it is equivalent to $f?|ff|\dots|\underbrace{f}_{x \text{ times}}$ which has an NFA mapping. 
%we can expand it into a standard regular expression form, for example
expanding it into a regular expression form; for example 
$f$\^{}$3$ is equivalent to $f?|ff|fff$. 
Consider the example of Figure~\ref{fig:intromotiv} and the
corresponding expression $(P|N)\!+~O?~R~O^\wedge 2~(P|N|U)+$.
Figure~\ref{fig:nfaEx} shows part of the corresponding NFA where
$q_8, q_9, \dots, q_{13}$ represent NFA states,
and edges are transitions based on MBF tags such as 
$P,$ and $N$.
Edges labeled with the empty string $\epsilon$ are non-deterministic.
%The expression uses operations $|$, $?$, $+$, and $\wedge$ to relate places {\tt P}, names of persons {\tt N}, relative positions {\tt R}, numerical terms {\tt U}, and other {\tt O}.

>>>>

For each MRE, 
\framework generates its equivalent non-deterministic finite automaton (NFA) in the typical manner~\cite{sipser2012introduction}.
%Each MRE operation has its equivalent representation in an NFA. 
We support the upto operation ($f$\^{}$x$), which is not directly 
supported in~\cite{sipser2012introduction}, by 
%it is equivalent to $f?|ff|\dots|\underbrace{f}_{x \text{ times}}$ which has an NFA mapping. 
%we can expand it into a standard regular expression form, for example
expanding it into a regular expression form; for example 
$f$\^{}$3$ is equivalent to $f?|ff|fff$. 
Consider the example of Figure~\ref{fig:intromotiv} and the
corresponding expression $(P|N)\!+~O?~R~O^\wedge 2~(P|N|U)+$.
Figure~\ref{fig:nfaEx} shows part of the corresponding NFA where
$q_8, q_9, \dots, q_{13}$ represent NFA states,
and edges are transitions based on MBF tags such as 
$P,$ and $N$.
Edges labeled with the empty string $\epsilon$ are non-deterministic.
%The expression uses operations $|$, $?$, $+$, and $\wedge$ to relate places {\tt P}, names of persons {\tt N}, relative positions {\tt R}, numerical terms {\tt U}, and other {\tt O}.
